---
output: 
  md_document:
    variant: markdown_github
---

# Predicting A Products Shipping Mode :package: w/ {tidymodels}

Having recently participated in the r4ds `{tidymodels}` bookclub, I decided to give data modeling a try. For this blog post, we use the Superstore dataset from Tableau. The dataset was found on the Tableau community forum and can found [here](https://community.tableau.com/s/question/0D54T00000C5vSDSAZ/global-superstore-data-file). I decide to use this dataset instead of the more traditional data sets to mix things up a bit. The Superstore data set records purchases from fictional customers regarding various products.

As is customary, we start by loading the necessary packages and data.

```{r setup,  message=FALSE, warning=FALSE}
library(tidyverse)
library(tidymodels)
library(janitor)
library(readxl)
library(lubridate)
library(ggthemes)
library(gt)
library(viridis)

orders <- read_excel("data/Global Superstore.xls", sheet = "Orders") %>% 
  clean_names()

month_lu <- month.abb %>% 
  tibble(.name_repair = ~c("month_abb")) %>% 
  mutate(month = seq(1,12,1),
         month_abb = factor(month_abb, levels = c("Jan", "Feb", "Mar", "Apr",
                                                  "May", "Jun", "Jul", "Aug",
                                                  "Sep", "Oct", "Nov", "Dec")))

#data source: https://community.tableau.com/s/question/0D54T00000C5vSDSAZ/global-superstore-data-file


knitr::opts_chunk$set(fig.align = 'center')

```


# Superstore Data

The superstore dataset consist of transactions for customers order, including single and bulk orders. In addition to each individual item, there are other transactional details like order and ship date, shipping mode, profit margin and many other items. Below you can see the complete list that is available

```{r superstore_names, echo=FALSE}
orders %>% 
  colnames()

```

The *main objective* of this post is to **predict a products shipping mode** based on a set of predictors.

Though all factors may be relevant in helping to predict the shipping mode of a customer, I decide to limit it to a few that I believe matter. Note that this decision is not based on any scientific research instead is my intuition, which may be off. The variables I decide to go with are *order date*, *shipping data*, *segment*, *shipping cost*, *order priority*, and *profit*.

```{r superstore_data}
head(orders) %>% 
  select(customer_id, order_date, ship_mode, segment,
         shipping_cost, order_priority, profit)
```

# Data Preparation

Prior to delving into some exploratory analysis, there are some preproceesing steps that we need to take care as to avoid errors when building our models.

The *first* part of our preproceesing is to create some new variables. Using `group_by()` on customer id and order date, we are able to count how many items were sent within a particular order. This may matter because a product that is part of a larger order may receive a faster shipping mode. The other variable we create is one that tells us in what month a product was shipped in. Using the `month()` function from the {lubridate} package we are able to extract the month.

The *second* part in our preprocessing is to convert some of the character variables into numerical values. We apply this to the segment, shipping mode, and order priority variable. Later on we will be using the {recipes} package to further process these variables into a form that our models will comport with.


```{r tidy_data}
processed_orders <- orders %>% 
  select(customer_id, order_date, ship_mode, segment,
         shipping_cost, order_priority, profit) %>% 
  group_by(customer_id, order_date) %>% 
  mutate(num_in_order = n()) %>% 
  ungroup() %>% 
  mutate(order_month = month(order_date),
         segment = case_when(segment == "Consumer" ~ 1,
                             segment == "Corporate" ~ 2,
                             TRUE ~ 3), #Home Office
         ship_mode = case_when(ship_mode == "Same Day" ~ 1,
                               ship_mode == "First Class" ~ 2,
                               ship_mode == "Second Class" ~ 3,
                               TRUE ~ 4), # Standard Class
         order_priority = case_when(order_priority == "Critical" ~ 1,
                                    order_priority == "High" ~ 2,
                                    order_priority == "Medium" ~ 3,
                                    TRUE ~ 4)) %>% #Low
  left_join(month_lu, by = c("order_month" = "month")) %>% 
  mutate_at(vars(ship_mode, segment, order_priority, order_month), ~as.factor(.)) %>% 
  select(-c(customer_id, order_date))
  
```

# Exploratory Analysis

Now that we have processed our data, we can begin exploring some of our predictors to see what kind of relationship they have with a products shipping mode.

## Number Of Items In A Order

Below we consider the relationship between the number of items in a order and the preferred method.

```{r explore_num_in_order}

processed_orders %>% 
  count(num_in_order, ship_mode) %>% 
  ggplot(aes(num_in_order, log(n), fill = ship_mode)) +
  geom_col() +
  scale_fill_tableau(name = "Shipping Method",
                     labels = c("Same Day", "First Class", 
                                "Second Class", "Standard Class")) +
  scale_y_continuous(limits = c(0, 40)) +
  scale_x_continuous(breaks = seq(1,14, 1)) +
  labs(
    x = "Number of items in a order",
    y = "Count (log10)",
    title = "Shipping Method For The Number Of Items In A Order",
    subtitle = "1 logged order = 10,000 orders"
  ) +
  theme(
    panel.grid = element_blank(),
    panel.background = element_blank(),
    plot.subtitle = element_text(size = 9),
    axis.ticks.x = element_blank(),
    axis.text = element_text(colour = "black")
  )
  
```

With there being a large positive skew, logging the count of orders also for a potential relationship to be observed. Not associated with our relationship of interest, but we see that there are many orders that content ten or less items per order. As for the number of items in an order pertains to shipping method, we see that "same day" shipping is less preferred as more items added to an order. The trend can be somewhat seen with "second class" and "standard class" shipping. As for the "first class" shipping, we see a ebb and flow in terms of their overall composition of total orders.

## Shipping Month

Exploring the distribution of shipping months for each shipping method is important to explore because of the possibility of seasonality. In the graphic below we can see that the frequency of when products are shipped usually occurs in the later months of the year, specifically during the festive months regardless of shipping method.

```{r explore_shipping_months}

processed_orders %>% 
  count(ship_mode, month_abb) %>% 
  group_by(ship_mode) %>% 
  mutate(ship_mode_percent = n/sum(n)) %>% 
  ungroup() %>% 
  ggplot(aes(ship_mode, fct_rev(month_abb), fill = ship_mode_percent)) +
  geom_tile() +
  geom_text(aes(label = round(ship_mode_percent * 100, 0))) +
  scale_fill_distiller(palette = "Spectral",
                       labels = percent,
                       name = "Shipping Mode \nPercent") +
  scale_x_discrete(labels = c("Same Day", "First Class", 
                              "Second Class", "Standard Class"),) +
  labs(
    x = "Shipping Method",
    y = "Order Month",
    title = "Most Frequent (%) Order Months For Each Shipping Mode"
  ) +
  theme(
    axis.ticks = element_blank(),
    axis.text = element_text(color = "black"),
    panel.grid = element_blank(),
    panel.background = element_blank()
  )

```

Going forward, we may have to consider how to account for seasonal difference in our model. One approach we could take is creating a dummy variable that designates a December shipment versus a non December shipment. Another approach is to split the year into quarters. Finally the third approach we could take is creating groups of equal size as to control for seasonality.

## Shipping Cost

The last piece of data we will explore concerns the shipping cost for each of the different shipping methods. To best visualize this relationship, I decide to go with a density plot that will better display the probability distribution. With the distribution of the shipping cost being positively skewed, we need to account for it by logging by base 10 all the values. For example if the shipping cost were 10, than the new logged valued would be 1 (`r log10(10)`).

```{r shipping_cost}

processed_orders %>% 
  mutate(shipping_cost = log10(shipping_cost)) %>% 
  ggplot(aes(shipping_cost, colour = ship_mode)) +
  geom_density(size = 0.8) +
  scale_colour_tableau(name = "Shipping \nMode",
                       labels = c("Same Day", "First Class", 
                                  "Second Class", "Standard Class")) +
  scale_y_continuous(limits = c(0, .75),
                     breaks = seq(0, .75, .25)) +
  labs(
    title = "Log10 Density Plot For The Shipping Cost For Each Shipping Mode",
    x = "Shipping Cost",
    y = "Density"
  ) +
  theme(
    axis.ticks = element_blank(),
    panel.grid = element_blank(),
    panel.background = element_blank(),
    legend.key = element_blank()
  )

```

Considering the shipping cost, we can see that generally the shipping cost distribution for the different shipping modes are the same. For those reasons it would seem as if shipping cost may not play as in important role in helping use predict the shipping mode of an item. 

Having explored some of the predictors, we are ready to start building our model.

# Creating A Recipe

The {recipes} package offers a easy and reproducible way to preprocess data to be able to fit a new model. I will not go into full detail about what all the {recipes} package can do but for more information visit the {recipes} [page](https://recipes.tidymodels.org/index.html).

It has been my experience that models are particular in the way that variables are structured, for that reason the {recipes} package is great at formatting predictors in a the right structure. In the following code I start by removing the month abbreviations because they do not make 

```{r recipe}
model_data <- processed_orders %>% 
  select(-month_abb)

model_recipe <- recipe(ship_mode ~ ., data = model_data) %>% 
  step_normalize(c(shipping_cost, profit))
  
```

# Building models

```{r splitting}

model_split <- initial_split(model_data)
model_training <- training(model_split)
model_testing <- testing(model_split)

```


```{r model_build}



```




# Reporting Results

# Conclusions
