---
output: 
  md_document:
    variant: markdown_github
---

# Predicting A Customers Shipping Mode :package:

Having seen recent articles and tweets regarding the {tidymodels} package, I decided to give it a try myself. Today I decide to use the superstore dataset that is commonly used when working in Tableau. The superstore data records purchases from fictional customers regarding various products.

As is customary, we start by loading the necessary packages and data.

```{r setup,  message=FALSE, warning=FALSE}
library(tidyverse)
library(tidymodels)
library(janitor)
library(readxl)

orders <- read_excel("data/Global Superstore.xls", sheet = "Orders") %>% 
  clean_names()

#data source: https://community.tableau.com/s/question/0D54T00000C5vSDSAZ/global-superstore-data-file

```

For this post, we use the Superstore dataset from Tableau. The dataset was found on the Tableau community forum and can found [here](https://community.tableau.com/s/question/0D54T00000C5vSDSAZ/global-superstore-data-file). 


# Superstore Data

The superstore dataset consist of transactions (fictional) for customers order which can be a single item or multiple items. In addition to each individual item, there are other transactional details like order and ship date, shipping mode, profit margin and many other items. 

```{r superstore_data}

head(orders) %>% 
  select(customer_id, order_date, ship_date, ship_mode, segment,
         shipping_cost, order_priority, profit)

```

The *main objective* of this post is to **predict a customers shipping mode** based on a set of predictors.

# Exploratory Analysis


# Creating A Recipe

# Building models

# Reporting Results

# Conclusions
